Analysis of the properties of probabilistic models in learning problems with an expert\thanks{The reported study was funded by RFBR according to the research projects 20-37-90050, 19-07-01155 and NTI project 13/1251/2018.}

### 2021-01-02 paper/Bazarova2020Springer/BliendedManuscript.tex
article

\begin{figure}[h!]
     \includegraphics[width=\textwidth]{figures/explanation}
     \caption {Example: a) expert information of the first expert; b) baseline data; c) expert information of the second expert}
    \label{intro:fig2}
\end{figure}

@@

\begin{figure}[h!]
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/real_image}\label{intro:fig1:real}} 
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/outline_image}\label{intro:fig1:outer}} 
\caption{An example of the image of the iris of the eye and its outline representation: a) the image of the iris of the eye; b) contour image of the iris and approximating the given image of the circumferences}
\label{intro:fig1}
\end{figure}

@@

\subsection{ Experiment with circumstances }
\begin{figure}[h!]
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/900.eps}} 
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/901.eps}}
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/902.eps}}

@@

\begin{figure}[h]
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/900noise.eps}} 
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/901noise.eps}}\\
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/902noise.eps}}

@@

\subsection{ Experiment with different noise levels and variance of the prior distribution }
\begin{figure}[h!t]
\includegraphics[width=0.8\textwidth]{figures/beta_gamma}
\caption{ The result of the approximation for data with different noise levels~$\beta$ and on the variance of the prior distribution~$\gamma$}
\label{ce:fig6}
\end{figure}

\begin{figure}[h!t]
\includegraphics[width=0.5\textwidth]{figures/3dplot}
\caption{Dependence of models on the noise level~$\beta$ in the data, as well as on the variance of the prior distribution~$\gamma$}
\label{ce:fig5}
\end{figure}
In this part of the experiment, we analyze the quality of approximation~$S$ on the noise level~$\beta$ in the data and on the parameter of a priori distributions~$\gamma$. The sample is obtained as followsfirst, two vectors of parameters are randomly selected~$\mathbf{w}^\text{true}_{1}$ and~$\mathbf{w}^\text{true}_{2}$ are  coefficients of two parabolas. The vectors~$\mathbf {w}^\text {true}_{1} $ and~$\mathbf{w}^\text {true}_{2} $ are used to generate points~$x_i$ and~$y_i$ with normal noise added~$\varepsilon\sim\mathcal {N} \bigr(0,\beta\bigr)$. When training a multi-model, the prior distribution of parameters is considered~$\mathbf{w}_1\sim\mathcal{N}\bigr(\mathbf{w}^\text{true}_{1}, \gamma\mathbf{I}\bigr),\mathbf{w}_2\sim\mathcal{N}\bigr(\mathbf{w}^\text{true}_{2}, \gamma\mathbf{I}\bigr)$.

@@

\subsection{Iris approximations }
\begin{figure}[h!]
	\subfloat[]{\includegraphics[height = 0.17\textheight]{figures/not_prior_real_example}} 
	\subfloat[]{\includegraphics[height = 0.17\textheight]{figures/prior_real_example}}
	\subfloat[]{\includegraphics[height = 0.17\textheight]{figures/prior_regular_real_example}} 
\caption{Visualization of the approximation of the iris: a) if the $ R_0 $ regularizer is specified; b) if the $ R_1 $ regularizer is specified; b) if the $ R_2 $ regularizer is specified}
\label{ce:fig6}
\end{figure}

\begin{figure}
     \includegraphics[width=\textwidth]{figures/experiment_real_not_prior}\\
     \caption{Visualization of the multi-model convergence process in the case of a regularizer~$R_0$}
    \label{ce:fig7}
\end{figure}

\begin{figure}
     \includegraphics[width=\textwidth]{figures/experiment_real_prior}
     \caption{Visualization of the multi-model convergence process in the case of a regularizer~$R_1$}
    \label{ce:fig8}
\end{figure}

\begin{figure}
     \includegraphics[width=\textwidth]{figures/experiment_real_regular}
     \caption{Visualization of the multi-model convergence process in the case of a regularizer~$R_2$}
    \label{ce:fig9}
\end{figure}

>>>>

\begin{figure}[h!]
     \includegraphics[width=\textwidth]{explanation}
     \caption {Example: a) expert information of the first expert; b) baseline data; c) expert information of the second expert}
    \label{intro:fig2}
\end{figure}

@@

\begin{figure}[h!]
	\subfloat[]{\includegraphics[height = 0.2\textheight]{real_image}\label{intro:fig1:real}} 
	\subfloat[]{\includegraphics[height = 0.2\textheight]{outline_image}\label{intro:fig1:outer}} 
\caption{An example of the image of the iris of the eye and its outline representation: a) the image of the iris of the eye; b) contour image of the iris and approximating the given image of the circumferences}
\label{intro:fig1}
\end{figure}

@@

\subsection{ Experiment with circumstances }
\begin{figure}[h!]
	\subfloat[]{\includegraphics[height = 0.2\textheight]{900.eps}} 
	\subfloat[]{\includegraphics[height = 0.2\textheight]{901.eps}}
	\subfloat[]{\includegraphics[height = 0.2\textheight]{902.eps}}

@@

\begin{figure}[h]
	\subfloat[]{\includegraphics[height = 0.2\textheight]{900noise.eps}} 
	\subfloat[]{\includegraphics[height = 0.2\textheight]{901noise.eps}}\\
	\subfloat[]{\includegraphics[height = 0.2\textheight]{902noise.eps}}

@@

\subsection{ Experiment with different noise levels and variance of the prior distribution }
\begin{figure}[h!t]
\includegraphics[width=0.8\textwidth]{beta_gamma}
\caption{ The result of the approximation for data with different noise levels~$\beta$ and on the variance of the prior distribution~$\gamma$}
\label{ce:fig6}
\end{figure}

\begin{figure}[h!t]
\includegraphics[width=0.5\textwidth]{3dplot}
\caption{Dependence of models on the noise level~$\beta$ in the data, as well as on the variance of the prior distribution~$\gamma$}
\label{ce:fig5}
\end{figure}
In this part of the experiment, we analyze the quality of approximation~$S$ on the noise level~$\beta$ in the data and on the parameter of a priori distributions~$\gamma$. The sample is obtained as followsfirst, two vectors of parameters are randomly selected~$\mathbf{w}^\text{true}_{1}$ and~$\mathbf{w}^\text{true}_{2}$ are  coefficients of two parabolas. The vectors~$\mathbf {w}^\text {true}_{1} $ and~$\mathbf{w}^\text {true}_{2} $ are used to generate points~$x_i$ and~$y_i$ with normal noise added~$\varepsilon\sim\mathcal {N} \bigr(0,\beta\bigr)$. When training a multi-model, the prior distribution of parameters is considered~$\mathbf{w}_1\sim\mathcal{N}\bigr(\mathbf{w}^\text{true}_{1}, \gamma\mathbf{I}\bigr),\mathbf{w}_2\sim\mathcal{N}\bigr(\mathbf{w}^\text{true}_{2}, \gamma\mathbf{I}\bigr)$.

@@

\subsection{Iris approximations }
\begin{figure}[h!]
	\subfloat[]{\includegraphics[height = 0.17\textheight]{not_prior_real_example}} 
	\subfloat[]{\includegraphics[height = 0.17\textheight]{prior_real_example}}
	\subfloat[]{\includegraphics[height = 0.17\textheight]{prior_regular_real_example}} 
\caption{Visualization of the approximation of the iris: a) if the $ R_0 $ regularizer is specified; b) if the $ R_1 $ regularizer is specified; b) if the $ R_2 $ regularizer is specified}
\label{ce:fig6}
\end{figure}

\begin{figure}
     \includegraphics[width=\textwidth]{experiment_real_not_prior}\\
     \caption{Visualization of the multi-model convergence process in the case of a regularizer~$R_0$}
    \label{ce:fig7}
\end{figure}

\begin{figure}
     \includegraphics[width=\textwidth]{experiment_real_prior}
     \caption{Visualization of the multi-model convergence process in the case of a regularizer~$R_1$}
    \label{ce:fig8}
\end{figure}

\begin{figure}
     \includegraphics[width=\textwidth]{experiment_real_regular}
     \caption{Visualization of the multi-model convergence process in the case of a regularizer~$R_2$}
    \label{ce:fig9}
\end{figure}
